The NEOCP in the Era of LSST

### 2022-05-15 paper/sections/methods.tex
talk about checks of hybrid, make lipsum grey

\subsubsection{Assessing quality of hybrid catalogue}

\subsection{Simulated Observations}
\subsection{\dig{} Score Calculation}
\subsection{LSST Discovery probability}
\todo{need to actually do this}

% \url{https://www.astroml.org/modules/generated/astroML.density_estimation.KNeighborsDensity.html#astroML.density_estimation.KNeighborsDensity}

% \url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.cKDTree.query.html#scipy.spatial.cKDTree.query}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{density_comparisons.png}
    \caption{A comparison of the density of \mpco{} objects with those objects that were matched in \sss{} by our hybrid catalogue pipeline.}
\end{figure}

>>>>

\subsubsection{Assessing quality of hybrid catalogue}
It is essential that the underlying distributions of the hybrid catalogue do not differ significantly from S3M so that we still accurately reproduce the solar system. In Figure~\ref{fig:hybrid_vs_s3m_dists}, we show the distributions of the absolute magnitude and six orbital elements in both the hybrid catalogue and S3M. It is evident that the distributions are essentially identical.

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{hybrid_vs_s3m_distributions.png}
    \caption{A comparison of the parameter distributions of S3M and the hybrid catalogue.}
    \label{fig:hybrid_vs_s3m_dists}
\end{figure*}

As a further check, we compared MPCORB to the objects that were removed from S3M, since these should have nearly identical distributions. In Figure~\ref{fig:density_compare}, we show a comparison of the densities for the heliocentric $x$ and $y$ and it is clear that these distributions are left unchanged in the hybrid catalogue.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{density_comparisons.png}
    \caption{A comparison of the density of \mpco{} objects with those objects that were matched in \sss{} by our hybrid catalogue pipeline.}
    \label{fig:density_compare}
\end{figure}

\subsection{Simulated Observations}
\subsection{\dig{} Score Calculation}
\subsection{LSST Discovery probability}
\todo{}
